\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-20 gwnnDraft02.tex
a few quick changes

In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom. Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons \draftnote{can't have quarks and baryons} of these sectors can also be relativistic. In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom. The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances. The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models. 

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

@@

>>>>

In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom. Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and heavy bosons of these sectors can also be relativistic. In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom. The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances. The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models. 

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

@@

Gravitational wave signals continue to grow in importance as phenomenological si

We can think of these results providing 
This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors

Further, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.

Questions, of course, still remain: how can the estimations of $\alpha$ and $\beta \ H$ be improved?
